\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-06 fully-abstract-comp/popl2019/paper.tex
Added extra explanation of duplication.

\todo[inline]{If target cap. machine is introduced before this section, then revisit/delete this section.}
% Informally explain how we prevent this using linear capabilities
As the examples illustrate, the standard memory and object-like capabilities (sealed capabilities) do not provide sufficient guarantees to enforce LSE and WBCF.
The problem is essentially that the stack and return pointers that a callee receives from a caller remain in effect after their intended lifetime: either when the callee has already returned or when they have themselves invoked other code. 
Linear capabilities offer a form of revocation that can be used to prevent this from happening.

>>>>

\todo[inline]{If target cap. machine is introduced before this section, then revisit/delete this section.}
% Informally explain how we prevent this using linear capabilities
As the examples illustrate, the standard memory and object-like capabilities (sealed capabilities) do not provide sufficient guarantees to enforce LSE and WBCF.
The problem is essentially that the stack and return pointers that a callee receives from a caller remain in effect after their intended lifetime: either when the callee has already returned or when they have themselves invoked other code. 
Linear capabilities offer a form of revocation\footnote{Revocation in the sense that if we hand out a linear capability and later get it back, then the receiver no longer has it or a copy of it as it is non-duplicable.} that can be used to prevent this from happening.
